Optimal Task Phasing for End-To-End Latency in Harmonic and Semi-Harmonic Automotive Systems

### 2024-09-25 paper.tex
motivating example

\usepackage{tikz}
\usetikzlibrary{arrows,decorations.markings, positioning}
\usepackage{subcaption}
\usepackage{tabu}

@@

%% PAPER SPECIFIC:
\usetikzlibrary{patterns}

@@

@@

>>>>

\usepackage{tikz}
\usetikzlibrary{arrows,decorations.markings, positioning}
% \usepackage{subcaption}
\usepackage{tabu}

@@

%% PAPER SPECIFIC:
\usetikzlibrary{patterns}
\ifCLASSOPTIONcompsoc
	\usepackage[caption=false,font=normalsize,labelfont=sf,textfont=sf]{subfig}
\else
	\usepackage[caption=false,font=footnotesize]{subfig}
\fi

@@

	\mario{This is the first work that exploits partitioned job chains analytically after their initial exploration in \cite{DBLP:conf/ecrts/GunzelTCBC23}.}

@@

	In this section, we demonstrate the impact of task phasing on the end-to-end latency. 
	To that end, we consider an example cause-effect chain $E = (\tau_1 \to \tau_2 \to \tau_3)$ with 
	\begin{itemize}
		\item $\tau_1,\tau_3 \in \mathit{Per}(10)$
		\item $\tau_2 \in \mathit{Per}(1)$.
	\end{itemize}

	The typical approach of making the task set synchronous, i.e., $\tau_1, \tau_2, \tau_3 \in \mathit{Phase}(0)$ leads to the schedule depicted in Figure

	\begin{figure}
		\centering
		\subfloat[Synchronous: $\lat(E) = 40$.]{
		\footnotesize
		\begin{tikzpicture}[yscale=0.22, xscale=0.2]

				\timeline{0}{41}{}
				% no labelling

				% \exec[fill=black!30]{0}{2}
				% \exec{2}{4}
				\exec[fill=black!30]{0}{10}
				\exec[fill=black!30]{10}{20}
				\exec{20}{30}
				\exec{30}{40}

				\timeline{0}{41}{}
				% \labelling{0}{13}{2}{0}

				\exec{0}{1}
				\exec{1}{2}
				\exec{2}{3}
				\exec{3}{4}
				\exec{4}{5}
				\exec{5}{6}
				\exec{6}{7}
				\exec{7}{8}
				\exec{8}{9}
				\exec{9}{10}
				\exec{10}{11}
				\exec{11}{12}
				\exec{12}{13}
				\exec{13}{14}
				\exec{14}{15}
				\exec{15}{16}
				\exec{16}{17}
				\exec{17}{18}
				\exec{18}{19}
				\exec{19}{20}

				\exec[fill=black!30]{20}{21}
				\exec{21}{22}
				\exec{22}{23}
				\exec{23}{24}
				\exec{24}{25}
				\exec{25}{26}
				\exec{26}{27}
				\exec{27}{28}
				\exec{28}{29}
				\exec{29}{30}

				\exec{30}{31}
				\exec{31}{32}
				\exec{32}{33}
				\exec{33}{34}
				\exec{34}{35}
				\exec{35}{36}
				\exec{36}{37}
				\exec{37}{38}
				\exec{38}{39}
				\exec{39}{40}
			\end{scope}

				\timeline{0}{41}{}
				\labelling{0}{40}{2}{0}

				% \exec{0}{4}
				\exec{0}{10}
				\exec{10}{20}
				\exec{20}{30}
				\exec[fill=black!30]{30}{40}

			\end{scope}
			\end{tikzpicture}	
		}\label{fig:motivation:synchronous}
		\\
		\subfloat[Optimized phasing: $\lat(E) = 31$]{
		\footnotesize
		\begin{tikzpicture}[yscale=0.22, xscale=0.2]

				\timeline{0}{41}{}
				% no labelling

				% \exec[fill=black!30]{0}{2}
				% \exec{2}{4}
				\exec[fill=black!30]{0}{10}
				\exec[fill=black!30]{10}{20}
				\exec{20}{30}
				\exec{30}{40}

				\timeline{0}{41}{}
				% \labelling{0}{13}{2}{0}

				\exec{0}{1}
				\exec{1}{2}
				\exec{2}{3}
				\exec{3}{4}
				\exec{4}{5}
				\exec{5}{6}
				\exec{6}{7}
				\exec{7}{8}
				\exec{8}{9}
				\exec{9}{10}
				\exec{10}{11}
				\exec{11}{12}
				\exec{12}{13}
				\exec{13}{14}
				\exec{14}{15}
				\exec{15}{16}
				\exec{16}{17}
				\exec{17}{18}
				\exec{18}{19}
				\exec{19}{20}

				\exec[fill=black!30]{20}{21}
				\exec{21}{22}
				\exec{22}{23}
				\exec{23}{24}
				\exec{24}{25}
				\exec{25}{26}
				\exec{26}{27}
				\exec{27}{28}
				\exec{28}{29}
				\exec{29}{30}

				\exec{30}{31}
				\exec{31}{32}
				\exec{32}{33}
				\exec{33}{34}
				\exec{34}{35}
				\exec{35}{36}
				\exec{36}{37}
				\exec{37}{38}
				\exec{38}{39}
				\exec{39}{40}
			\end{scope}

				\timeline{0}{41}{}
				\labelling{0}{40}{2}{0}

				% \exec{0}{4}
				\exec{1}{11}
				\exec{11}{21}
				\exec[fill=black!30]{21}{31}
				\execopen{31}{40}

			\end{scope}
			\end{tikzpicture}	
		}\label{fig:motivation:phasing}
		\caption{Motivating example. The longest $1$-partitioned job chain is marked in gray. Changing the phase of task $\tau_3$ from $0$ to $1$ improves the end-to-end latency by $22.5\%$.}
		\label{fig:motivation}
	\end{figure}
